The Influence of Radial Drift and Gas Accretion on the C/O Ratio in Protoplanetary Disks

### 2015-09-30 Postdoc Applications/AnaMariaPisoResume.tex
update

\section{\sc Education}
{\bf Harvard University}, Cambridge, MA \\
\begin{list1}
\vspace{-0.1in}
\item[] Ph.D., Astronomy \& Astrophysics, May 2016 (expected)
\item[] Advisor: Dr. Karin \"Oberg 
\item[] Thesis Topic: ``The Role of Disk Volatile Chemistry and Dynamics in Shaping the Compositions of Nascent Planets''
\end{list1}
{\bf Harvard University}, Cambridge, MA \\
\begin{list1}
\vspace{-0.1in}
\item[] A.M., Astronomy \& Astrophysics, May 2013
\item[] Advisor: Dr. Ruth Murray-Clay
\item[] Research Exam Project: ``On the Minimum Core Mass for Giant Planet Formation''
\end{list1}
{\bf Massachusetts Institute of Technology}, Cambridge, MA\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] S.B., Physics,  June 2010 \,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\, Major GPA: 4.6/5.0
\item[] S.B., Mathematics, June 2010\,\,\,\, Major GPA: 4.8/5.0
\end{list1}

@@

\item[] {\bf Research assistant} \hfill {\bf June 2009 - August 2009}
%{\bf Harvard-Smithsonian Center for Astrophysics} \hfill \textit{Cambridge, MA}
\begin{list1}
%\vspace{-0.1in}
\item[] Viena University of Technology (TU Wien) \hfill \textit{Vienna, Austria}
\item[] Project: Exact relativistic viscous fluid solutions in near horizon extremal Kerr background
\item[] Advisor: Dr. Daniel Grumiller \\
\end{list1}

>>>>

\section{\sc Education}
{\bf Harvard University}, Cambridge, MA \\
\begin{list1}
\vspace{-0.1in}
\item[] Ph.D., Astronomy \& Astrophysics, May 2016 (expected)
\item[] Advisor: Dr. Karin \"Oberg 
\item[] Thesis Topic: ``The Effect of Disk Chemistry and Dynamics in Shaping Volatile Snowlines''   
\end{list1}
{\bf Harvard University}, Cambridge, MA \\
\begin{list1}
\vspace{-0.1in}
\item[] A.M., Astronomy \& Astrophysics, May 2013
\item[] Advisor: Dr. Ruth Murray-Clay
\item[] Research Exam Project: ``On the Minimum Core Mass for Giant Planet Formation''
\end{list1}
{\bf Massachusetts Institute of Technology}, Cambridge, MA\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] S.B., Physics,  June 2010 \,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\, Major GPA: 4.6/5.0
\item[] S.B., Mathematics, June 2010\,\,\,\, Major GPA: 4.8/5.0
\end{list1}

@@

\item[] {\bf Research assistant} \hfill {\bf June 2009 - August 2009}
%{\bf Harvard-Smithsonian Center for Astrophysics} \hfill \textit{Cambridge, MA}
\begin{list1}
%\vspace{-0.1in}
\item[] Vienna University of Technology (TU Wien) \hfill \textit{Vienna, Austria}
\item[] Project: Exact relativistic viscous fluid solutions in near horizon extremal Kerr background
\item[] Advisor: Dr. Daniel Grumiller \\
\end{list1}
